Analysis of observational data, to calculate the Delayed-Tau model parameters

### 2025-03-16 presentations/presentation.qmd
zezas presentation

---
title: "Παρουσιαση πτυχιακης"
subtitle: ""
author: "Δημήτρης Παπαχριστόπουλος"
format:
  revealjs:
    theme: moon
    center: true
    smaller: true
    #embed-resources: true
    chalkboard: true 
    controls: true
    slide-number: true 
    revealjs-plugin: 
      - PdfExport
    bibliography: My_Library.bib
editor: 
  markdown: 
    wrap: sentence
---

>>>>

---
title: "Παρουσιαση πτυχιακης"
subtitle: ""
author: "Δημήτρης Παπαχριστόπουλος"
format:
  revealjs:
    theme: moon
    center: true
    smaller: true
    #embed-resources: true
    chalkboard: true 
    controls: true
    slide-number: true 
    revealjs-plugin: 
      - PdfExport
editor: 
  markdown: 
    wrap: sentence
---

### 2025-03-16 presentations/presentation_chatzidimitriou.qmd
zezas presentation

---
title: "Τιτλος"
subtitle: ""
author: "Δημήτρης Παπαχριστόπουλος"
format:
  revealjs:
    theme: moon
    #embed-resources: true
    controls: true
    slide-number: true 
    revealjs-plugin: 
      - PdfExport
    bibliography: My_Library.bib
editor: 
  markdown: 
    wrap: sentence
---

@@

# Τι ειναι το LCV

@@

![](figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}

@@

![](figure/Screenshot%20from%202024-12-07%2021-49-48.png){fig-align="center"}

@@

>>>>

---
title: "Analysis of observational data, to calculate the Delayed-Tau model parameters"
author: "Δημήτρης Παπαχριστόπουλος"
format:
  revealjs:
    theme: moon
    #embed-resources: true
    controls: true
    slide-number: true 
    revealjs-plugin: 
      - PdfExport
editor: 
  markdown: 
    wrap: sentence
---

@@

# Τι ειναι το Local Cosmological Volume

@@

![](../figure/log_SFR_FUV_Ha.png){fig-align="center" width="500"}

@@

![](../figure/Screenshot%20from%202024-12-07%2021-49-48.png){fig-align="center"}

@@

![](../compare/quickplots/SFR.png){fig-align="center"}
